---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include=FALSE}
knitr::opts_chunk$set(warning=FALSE, comment="")
library(tidyverse)
library(magrittr)
```

## Data
```{r}
fn <- "snapshot.csv"
snapshot <- readr::read_csv(fn, col_types=c("ccdcc"))
snapshot$balance <- as.integer(snapshot$balance)
summary(snapshot)
```

## Seed
```{r}
block <- 16761269 # https://etherscan.io/block/16761269
block_hash <- "0xe3b7ca157dd44d9e988fdc20a5b69d836817f693f5577330cd2ea79ba856d86d"
# Convert block hash to ASCII
# Take the sum over integer vector to set seed
seed <- sum(utf8ToInt(block_hash))
cat("Seed:", seed, "\n")
```

## Code
```{r}
subtract_multi <- function(x, y) {
  for (i in y) {
    where <- match(i, x)
    if (!is.na(where)) {
      x <- x[-where]
    }
  }
  return(x)
}

pick <- function(df,
                 contracts=c(),
                 address_remove=NULL,
                 address_subtract=NULL,
                 address_max=Inf,
                 address_pick=NA,
                 address_replace=FALSE) {

  df <- df %>%
    dplyr::filter(name %in% contracts) %>%
    dplyr::filter(!(address %in% address_remove))
  
  df_by_address <- df %>%
    dplyr::group_by(address) %>%
    dplyr::summarise(
      balance = ifelse(sum(balance) <= address_max, sum(balance), address_max)
    )
  
  pool <- df_by_address %>%
    dplyr::arrange(address) %>%
    dplyr::select(address, balance) %>%
    purrr::pmap(function(address, balance) {
      base::rep(address, balance)
    }) %>%
    unlist() %>%
    subtract_multi(address_subtract)
  
  if (is.na(address_pick)) {
    return(pool)
  } else {
    return(base::sample(pool, size=address_pick, replace=address_replace))
  }
}

tally <- function(x) {
  if (length(x) > 0) {
    unlist(x) %>%
    data.frame(address = .) %>%
    dplyr::group_by(address) %>%
    dplyr::summarise(
      amount = n()
    ) %>%
    dplyr::arrange(desc(amount), address)
  }
}
```

```{r}
base::set.seed(seed)

address_remove <- c(
  "0x3a3548e060be10c2614d0a4cb0c03cc9093fd799",
  "0xc6400a5584db71e41b0e5dfbdc769b54b91256cd",
  "0x4b76837f8d8ad0a28590d06e53dcd44b6b7d4554",
  "0x0887773b5f43c58f0da7bd0402fc2d49482eb845",
  "0xcda72070e455bb31c7690a170224ce43623d0b6f",
  "0x41a322b28d0ff354040e2cbc676f0320d8c8850d",
  "0x000000000000000000000000000000000000dead"
)

hodlers_remove <- c(
  ""
)

airdrop_memes_all   <- pick(snapshot, contracts=c("memes_full_bothSZNs"),address_remove=address_remove, address_pick=12,address_max=1)
airdrop_memes_szn2  <- pick(snapshot, contracts=c("memes_full_SZN2"),address_remove=address_remove,address_subtract=airdrop_memes_all,address_pick=9,address_max=1)
airdrop_gradient    <- pick(snapshot, contracts=c("gradient"),address_pick=9, address_max=1)
airdrop_tokyoluv    <- pick(snapshot, contracts=c("SuperRare","SuperRare2","SuperRare3","Foundation","HYPERREALITY","ShapesofTokyo","TokyoluvCollection"), address_remove=address_remove,address_pick=30,address_max=1)

allow_tokyoluv_singles  <- pick(snapshot, contracts=c("SuperRare","SuperRare2","SuperRare3","Foundation","HYPERREALITY","ShapesofTokyo","TokyoluvCollection","NeonNoirTokyo"), address_remove=address_remove, address_subtract=airdrop_tokyoluv,address_max=1)
allow_tokyoluv_editions <- pick(snapshot, contracts=c("NeonNoirTokyo","TokyoluvCollectionEditions","FishyEditions","CapsuleEditions","TOKYOLUVEDITIONS","DokiDokiEditions","Decal"), address_remove=address_remove, address_subtract = c(airdrop_tokyoluv,allow_tokyoluv_singles),address_pick=400,address_max=1)
allow_gradient_phase1   <- pick(snapshot, contracts=c("gradient"), address_subtract=airdrop_gradient,address_max=1)
allow_memes_1_phase1    <- pick(snapshot, contracts=c("memes_full_bothSZNs"), address_remove=address_remove, address_subtract = c(airdrop_memes_all, airdrop_memes_szn2),address_max=1)
allow_memes_2_phase1    <- pick(snapshot, contracts=c("memes_full_SZN2"), address_remove=address_remove, address_subtract = c(airdrop_memes_all, airdrop_memes_szn2,allow_memes_1_phase1),address_max=1)
allow_memes_3_phase1    <- pick(snapshot, contracts=c("memes_top_500"), address_remove=address_remove, address_subtract = c(airdrop_memes_all, airdrop_memes_szn2,allow_memes_1_phase1,allow_memes_2_phase1),address_pick=100,address_max=1)
allow_memes_4_phase1    <- pick(snapshot, contracts=c("memes_random_50"), address_remove=address_remove, address_subtract = c(airdrop_memes_all, airdrop_memes_szn2,allow_memes_1_phase1,allow_memes_2_phase1,allow_memes_3_phase1),address_pick=50,address_max=1)

allow_tokyoluv_phase2   <- pick(snapshot, contracts=c("TokyoluvCollectionEditions","FishyEditions","CapsuleEditions","TOKYOLUVEDITIONS","DokiDokiEditions","Decal"), address_remove=address_remove, address_subtract = c(airdrop_tokyoluv,allow_tokyoluv_singles,allow_tokyoluv_editions),address_max=1)
allow_raw               <- pick(snapshot, contracts=c("raw"), address_remove=address_remove,address_max=1)
allow_singles           <- pick(snapshot, contracts=c("65291/1s"), address_remove=address_remove,address_max=1)
allow_memes_phase2      <- pick(snapshot, contracts=c("memes_top_500"), address_remove=address_remove, address_subtract = c(airdrop_memes_all, airdrop_memes_szn2,allow_memes_1_phase1,allow_memes_2_phase1,allow_memes_3_phase1,allow_memes_4_phase1),address_max=1)

```


## Airdrop Memes Both SZNs
```{r}
c(airdrop_memes_all) %>%
tally() %T>%
readr::write_csv(file="airdrop_memes_12_both_szns.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Airdrop Memes SZN2
```{r}
c(airdrop_memes_szn2) %>%
tally() %T>%
readr::write_csv(file="airdrop_memes_9_szn2.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Airdrop Gradients
```{r}
c(airdrop_gradient) %>%
tally() %T>%
readr::write_csv(file="airdrop_gradient.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Airdrop Artist
```{r}
c(airdrop_tokyoluv) %>%
tally() %T>%
readr::write_csv(file="airdrop_artist.csv", col_names=FALSE) %>%
print(n=Inf)
```




## Allow Artist 1/1s Phase 1
```{r}
c(allow_tokyoluv_singles) %>%
tally() %T>%
readr::write_csv(file="allow_artist_singles_phase1.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Allow Artist Editions Phase 1
```{r}
c(allow_tokyoluv_editions) %>%
tally() %T>%
readr::write_csv(file="allow_artist_editions_phase1.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Allow Gradient Phase 1
```{r}
c(allow_gradient_phase1) %>%
tally() %T>%
readr::write_csv(file="allow_gradient_phase1.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Allow Memes 1 Phase 1 (Full Set Both SZNs)
```{r}
c(allow_memes_1_phase1) %>%
tally() %T>%
readr::write_csv(file="allow_memes_full_both_szns_phase1.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Allow Memes 2 Phase 1 (Full Set SZN2)
```{r}
c(allow_memes_2_phase1) %>%
tally() %T>%
readr::write_csv(file="allow_memes_full_szn2_phase1.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Allow Memes 3 Phase 1 (Top 500)
```{r}
c(allow_memes_3_phase1) %>%
tally() %T>%
readr::write_csv(file="allow_memes_random100_phase1.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Allow Memes 4 Phase 1 (Random 50 from remaining)
```{r}
c(allow_memes_4_phase1) %>%
tally() %T>%
readr::write_csv(file="allow_memes_random50_phase1.csv", col_names=FALSE) %>%
print(n=Inf)
```





## Allow Artist Phase 2
```{r}
c(allow_tokyoluv_phase2) %>%
tally() %T>%
readr::write_csv(file="allow_artist_phase2.csv", col_names=FALSE) %>%
print(n=Inf)
```


## Allow 6529
```{r}
c(allow_raw, allow_singles) %>%
tally() %T>%
readr::write_csv(file="allow_6529_phase2.csv", col_names=FALSE) %>%
print(n=Inf)
```

## Allow Memes Phase 2 (Remaining from Top 500)
```{r}
c(allow_memes_phase2) %>%
tally() %T>%
readr::write_csv(file="allow_memes_phase2.csv", col_names=FALSE) %>%
print(n=Inf)
```


## Versioning
```{r}
R.version$version.string
packageVersion("tidyverse")
packageVersion("magrittr")
```
